\documentclass[a4paper,11pt,english]{article}
\usepackage{.styles/basic}
\usepackage{.styles/envs}

%%%%%%% Title %%%%%%%%%%%%%%%%%%%%%%%%%%%
\title{\textbf{Algebraic Geometry} - Exercise Sheet 1}
\author{Tor Gjone \& Paul}

%%%%%%% Definitions %%%%%%%%%%%%%%%%%%%%%
\input{defs}

\newSimpleHeaderEnvironment{exercise}{Exercise }
\newSimpleHeaderEnvironment{solution}{Solution }

% \newColoredBoxEnvironment{exercise}{Exercise }{green!20}
% \newColoredBoxEnvironment{solution}{Solution }{blue!20}

\def\A{\mathbb{A}}
\DeclareMathOperator{\rad}{rad}
\DeclareMathOperator{\tr}{tr}

%%%%%%%% Content %%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}
\mmaketitle

\begin{exercise}[1]
Let $X$ be a finite CW-complex and $Y$ a space such that for every base point
$y \in Y$ and every number $i$ that is less than or equal to the dimension of
$X$ the set $\pi_i(Y, y)$ is finite. Show that the set $[X, Y]$ of homotopy
classes of maps from $X$ to $Y$ is finite.
\end{exercise} 

\begin{solution}[1] %\vspace{-.8cm}
We will be doing the proof in a number of steps.
\begin{itemize}
\item Suppose for now that we have already proved the statement for $Y$
path-connected. Let $X^i \subet X$,  denote the path-connected components of $X$ and
similarly $Y^j \subset Y$ the path-connected components of $Y$. Then, by
assumption, $[X^i,Y^j]$, the set of homotopy classes of maps from $X^i$ to
$Y^j$, is finite.

Consider a map $f: X \to Y$, then for each $X^i\subset X$, $f|_{X^i}$ most be
contained in one of the path-connected components of $Y$, say $Y^j$. So
$f|_{X^i}$ defines an element in $[f|_{X^i}^{Y^j}] \in [X^i, Y^j]$. 

Define the following map
\[ \Phi : [X, Y] \to \prod_{i, j} \left( [X^i, Y^j] \sqcup \{ \omega \} \right);
\quad  
f \mapsto \prod{i,j} [f|_{X^i}^{Y^j}], \]
where $[f|_{X^i}^{Y^j}] = \omega$, whenever $f(X^i) \cap Y^j = \emptyset$. We
want to show that this map is well-defined and injective, because if it is $[X,
Y]$ most be fine, since the co-domain is a finite product of finite elements and
thus finite.

Suppose $f, g: X \to Y$ are homotopy equivalent by some homotopy $H$, then
$H|_{X^i}$ defines a homotopy from $f|_{X^i}$ to $g|_{X^i}$. So $\Phi$ is
well-defined. 

Now suppose $f,g: X \to Y$ such that $\Phi([f]) = \Phi([g])$. Then $f|_X^i$ is
homotopy equivalent to $g|_{X^i}$ by some homotopy $H_i$ for all of the
path-connected components of $X$. Clearly we may defined $H: I\times X \to Y$
by $H|_{X_i} = H_i$, which defines a homotopy between $f$ and $g$.

\item
So we may now, in the more interesting part of the proof, suppose wlog. that
$Y$ is path-connected. The idea of the proof is to consider another set of
homotopy classes, that projects surjective onto $[X,Y]$, and show that this set
is finite, which would imply that $[X,Y]$ is also finite.

\newcommand{\pX}{\parital X}

Fix an element $y_0 \in Y$ and let $\pX \subset X$ denote the set of boundaries
in $X$, ie. $x \in \pX$ if and only if $x \in \partial D^i$ for some $i$-cell in
$X$. 
Let $(X,Y,y_0)$ denote the set of of maps $f: X \to Y$, such that $f(\pX) = \{
y_0\}$ (or alternatively, such that for any $i$-cell $D^i$ in $X$, $f(\partial
D^i) = \{ y_0 \}$. ) 
Let $f, g \in (X,Y,y_0)$, then a homotopy between $f$ and $g$ is a homotopy $H:
I \times X \to Y$ (ie. $H(0,-) = f$ and $H(1,-) = g$) such that $H(I, \pX) = \{
y_0 \}$. Then we will let $[X,Y,y_0]$ be the set of homotopy classes in
$(X,Y,y_0)$.

We now claim that for any map $f: X \to Y$ there exists a map $\tilde{f} \in
[f]$ such that $\tilde{f} \in (X, Y, y_0)$. We will come back to the proof of
the claim further down, but for now will take it to be true. Clearly every map
in $(X,Y,y_0)$ is in particular a map from $X \to Y$, so we may define a map $p
: (X,Y,y_0) \to [X,Y]$. Also every homotopy that fixes $\pX$ is in particular a
homotopy, so $p$ descends to define a map $p_* : [X,Y,y_0] \to [X,Y]$. Finally
the claim implies that this map $p_*$ is in fact surjective.

\item
We will now prove that $[X,Y,y_0]$ is finite.






\end{itemize}
\end{solution} 



\end{document}
