\documentclass[a4paper,11pt,english]{article}
\usepackage{.styles/basic}
\usepackage{.styles/envs}
\frenchspacing

\usepackage{circuitikz}

\usepackage{caption}
\usepackage{subcaption}

%%%%%%% Title %%%%%%%%%%%%%%%%%%%%%%%%%%%
\title{\textbf{Algebraic Topology} - Exercise Sheet 8}
\author{Tor Gjone (2503108) \& Michele Lorenzi (3461634)}

%%%%%%% Definitions %%%%%%%%%%%%%%%%%%%%%
\input{defs}

\newSimpleHeaderEnvironment{exercise}{Exercise }

\setlength{\parindent}{0cm}
\setlength{\parskip}{3pt}

\usepackage{enumerate}

\DeclareMathOperator{\holim}{holim}

% I keep adding \ in from of the P's. This makes sure I get an error.
\def\P{\undefined}

%%%%%%%% Content %%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}
\mmaketitle

\begin{exercise}[1]
\begin{enumerate}[(a)]

\item %a
Let $[\xi] \in \pi_m(\holim_n P_n)$. We have
\begin{equation}
\pi_m(q_k)([\xi]) = [q_k \circ \xi] \q\tand 
\Psi \circ \pi_m(q_{k+1}) ([\xi]) = (\omega_k)_\star [p_k \circ q_{k+1} \circ
\xi]
\end{equation}
where $q_k \circ \xi$ is a loop based at $\omega_k(0)$ and $p_k \circ q_{k+1}
\circ \xi$ a loop based at $\omega_k(1)$, both in $P_k$. 

By extending the second loop by $\omega_k$ (ie. applying $(\omega_k)_\star$)
both loops are based at $\omega_k(0)$.

We want to show that these two maps are base homotopic. 

Consider $\xi(-)_k : S^m \to P_k[0,k]$. We denote the adjoint map by 
$\hat \xi_k : S^m \times [0,1] \to P_k$. 
Then $\hat \xi_k$ defines an unbased homotopy from $q_k \circ \xi$ to $p_k \circ q_{k+1} \circ
\xi$. Indeed, for $x \in S^k$,
\begin{align*}
(q_k \xi)(x)_k &=& \xi(x)_k(0) = \hat \xi_k(x,0)& \q{\tand} \\
(p_k \circ q_{k+1} \circ \xi) (x) &=& p_k(\xi(x)_{k+1} (0)) = \xi(x)_k(1) = \hat
\xi_k(x,1)
\end{align*}

Furthermore 
\begin{equation}
\hat \xi_k (1,-) = \xi(1)_k = \omega_k. 
\label{eq:2}
\end{equation}

We define $H : S^m \times [0,1]$ 
\[ H(-,t) := (\omega_k|_{[0,t]})_\star (\hat \xi_k(-,t)). \]
%
%\todo{add a figure}Note that $H$ is continues by \pref{eq:2}. Then $H$ defines a based (at
$\omega_k(0)$) homotopy from $q_k \xi$ to $\omega_\star (p_k \circ q_{k+1}
\circ \xi)$. 

\item %b
Let $\xi = ([\xi_n])_{n\ge 0} \in \lim_n \pi_m(P_n, \omega_n(0))$, i.e. there is $[\xi_n] \in
\pi_m(P_n, \omega_n(0))$ such that $\Psi_n([\xi_{n+1}]) = [\xi_n]$ for all $n\ge
0$. 

Let $H_n : S^m \times [0,1] \to P_n$ be a homotopy realizing $(\omega_n)_\star
(p_n \circ \xi_{n+1}) \sim \xi_n$  (based at $\omega_n(0)$).

Since the homotopy is based, it factors through the quotient \[V = S^m \times [0,1] /
\left(\{x_0\} \times [0,1]\right)\]
($x_0\in S^m$ denotes the base point). Let
$H_n': V \to P_n$ be the map defined by $H_n$. 

By the construction of the conjugation $(\omega_n)_\star$, we may defines a
homeomorphism $h_n : S^m \times [0,1] \to V$, such that $\wtil H_n = H_n' \circ
h_n$ defines a homotopy from $\xi_n$ to $p_n \circ \xi$ and $\wtil H_n(x_0,-) =
\omega_n$. 

% Se figure \pref{fig:2} for a illustration of the construction in
% dimension $m=1$.
% \todo{add fig}

By the exponential adjunction $\til H_n$ defines a map $\bar H_n: S^m \to
P_n^{[0,1]}$. 

By the construction of $\bar H_n$, $\bar H_n(x_0) = \omega_n$ and $\bar H_{n+1}
(x)(1) = p( \xi_{n}(x) ) = p (\bar H_n(x)(0))$, so $\bar H = (\bar H_n)_{n \ge
0}$ represent an element in $\pi_m(\holim_n P_n,\omega)$.

Also $q_n (\bar H(x)) = \bar H_n(x)(0) = \xi_n (x)$ for all $x\in S^m$, so
$\pi_m(q_n)(\bar H) = \xi$.

\item %c

\end{enumerate}
\end{exercise}

\begin{exercise}[2]

(a) This follows from the third exercise on the second exercise sheet (specifically, the second point), since then we have that there is an isomorphism between $\pi_m(T,i_0(x_0))$, where $T$ is the mapping telescope, and $\colim_k\pi_m(X_k,x_k)$. Now, clearly when $n\ne m$ we have that the colimit is zero, otherwise it is the colimit of the sequence of groups given.

(b) $S^1$ is a $K(\Z,1)$ and the map $f$ induces multiplication by $n$, hence we need to find the colimit of the sequence:
\[\Z\xto{n}\Z\xto{n}\cdots\xto{n}\Z\xto{n}\cdots.\]
This is just $\Z[n^{-1}]$, the localization of the integers at $n$ (as an abelian group), and this can be easily seen by showing that there is a morphism from the colimit to the localization, using the universal property of the colimit, and then showing that it is an isomorphism.
\end{exercise}

\begin{exercise}[3]

Let $X = M_n(A)$ be a Moore space with $H_n(X,\Z) \cong A$. 
By the Hurewicz Theorem, $\pi_k(X) = 0$ for $k \le n-1$ and $\pi_n(X) = A$, so 
we may construct an Eilenberg-MacLane, space $\til X$, starting with $X$ and
inductively "kill" the higher homotopy groups. 

Since $\pi_k(X)$ is "correct" (that is, it's what we want of the final space) 
the first homotopy group we might need to kill is in dimension $k=n+1$. 
In order to kill this homotopy we attach $n+2$ cells to $X$, which by cellular
approximation does not effect the homology in dimension $n+1$ and lower.

Similarly, to kill the higher homotopy groups, we attach cells of one dimension
higher. So throughout the construction of $\til X$ the homology group in dimension
$n+1$ is unchanged so we may conclude that $H_{n+1}(\til X, \Z) H_{n+1}(X, \Z) = 0$. 

Finally, since the Eilenberg-MacLane space is unique up to homotopy we may
conclude that $H_{n+1}(K(A,n),\Z) = 0$ independently of the construction of
$K(A,n)$.

\end{exercise}

\end{document}
