\sheet 8

\def\op{\text{op}}

\begin{document}
\mmaketitle

\begin{exercise}[1]\ 

The category of spectra has a fibration structure by considering the stable equivalences as weak equivalences and the levelwise Serre fibrations as the fibrations. The verification of the axioms follows immediately from known properties of Serre fibrations, except for the second part of axiom (F3) which we saw in the lecture (proposition 3.16 in Qi's notes, with the due modifications).

At this point, we know we have a calculus of right fractions, which gives us the claim.

Ok, maybe this is cheating, but I cannot find a better way. I tried to follow the hint, i.e. the calculus of left fractions gives us an acyclic cofibration $\tau:N\xto{\sim} A$ and a morphism $f:M\to A$ such that $\phi=\gamma(\tau)^{-1}\circ\gamma(f)$ and we can take the homotopy pullback of the diagram $M\to A\xleftarrow{\sim}N$ and play with it a bit. For some reason everything I tried on this front was missing some step...
\end{exercise}


\begin{exercise}[2]\ 

Disclaimer: we solved the exercise for the usual definitions of pre-additive and additive, which I guess we read on the nLab, forgetting that Schwede gave different definitions. Now, additive categories turn out to be the same using the two definitions, while Schwede's pre-additive categories are not pre-additive in the usual sense... I don't think it is worth it to rewrite the exercise as Schwede's axioms are clearly self dual, are they not?

Suppose $C$ is a preadditive category. Then 
for any $f,g : A \to B$, define
\[ f^\op +_\op g^\op := (f + g)^\op. \]
Given $f,g : A \to B$ and $h,k : B \to C$, we have
\begin{align*}
h^\op \circ_\op (f^\op +_\op g^\op)  
&= ((f+g)\circ h)^\op \\
&= ((f\circ h) + (g\circ h))^\op \\
&= (h^\op \circ_\op f^\op) +_\op (h^\op \circ_\op g^\op)
\end{align*}
And similarly 
\[ (h^\op + k^\op) \circ_\op f^\op = (h^\op \circ_\op f^\op) +_\op (k^\op \circ_\op
f^\op) \]

Hence, given that the notion of zero object is clearly self dual, $C^\op$ is preadditive. 
Furthermore, if $C$ is additive, i. e. has finite coproducts. 
Since the coproduct is also a product, it also defines a coproduct in the
opposite category, and thus $C^\op$ is additive.
\end{exercise}


\begin{exercise}[3]\ 

\begin{enumerate}
\item[(T0)] 
If $(-f',-g',-h')$ is isomorphic to $(-f,-g,-h)$ (anti-distinguished) by the morphism $(a,b,c)$, then 
$(A,b,c)$ also defines an isomorphism from $(f', g',h')$ to $(f,g,h)$. So
$(f',g',h')$ is distinguished and thus $(-f', -g',-h')$ is anti-distinguished.

\item[(T1)]
For any morphism $-f$, there exists a distinguished $(f,g,h)$. So $(-f,-g,-h)$
is anti-distinguished.

\item[(T2)]
$(0,-\id_X,0)$ is isomorphic to $(0,\id_X,0)$ by $(0,\id_X, -\id_X)$. 
So $(0,-\id_X,0)$ is distinguished and thus $(0,\id_X,0)$ is
anti-distinguished.

\item[(T3)]
If $(f,g,h)$ is distinguished, then $(g,h,-\Sigma f)$ is distinguished. So 
$(-g,-h,\Sigma f)$ is anti-distinguished.

\item[(T4)]
This follows immediately from the T4 property of $\T$, and the fact that 
a square commutes iff and only if the square commutes after changing the sign of
the horizontal (or vertical) maps. ie.
\[ 
(-b) \circ f = f' \circ (-a)
\qq{\Leftrightarrow}
b \circ (-f) = (-f') \circ a
\qq{\Leftrightarrow}
b \circ f = f' \circ a \] 

\item[(T5)]
Let $f:A\to B$ and $f':B \to D$ be morphisms, then by (T5) (with $-f$ and $-f'$) for $\T$, we we can find the following diagram
%
\[ \begin{tikzcd}
A \ar[r, "-f"] \ar[d, equal] &
B \ar[r, "-g"] \ar[d, "-f'"] &
C \ar[r, "-h"] \ar[d, "x"] &
\Sigma A      \ar[d, equal]
\\
A \ar[r, "f'f"]              &
D \ar[r, "-g'"]  \ar[d, "-g''"] &
E \ar[r, "-h''"] \ar[d, "y"]  &
\Sigma A        \ar[d, "-\Sigma f"]
\\
&
F \ar[r, equal] \ar[d, "-h'"] &
F \ar[r, "-h'"] \ar[d, "(\Sigma g)\circ h'"]  &
\Sigma B    
\\
&
\Sigma B \ar[r, "-\Sigma g"] &
\Sigma C &
\end{tikzcd} \]
such that $(-f,-g,-h), (f'f,-g',-h''), (-f',-g'',-h')$ and $(x,y,(\Sigma
g)\circ h')$ are distinguished. 

By changing some of the signs an even number of signs in each square, we
preserve the commutativity. Doing so, we get the following commutative diagram

\[ \begin{tikzcd}
A \ar[r, "f"] \ar[d, equal] &
B \ar[r, "g"] \ar[d, "f'"] &
C \ar[r, "h"] \ar[d, "-x"] &
\Sigma A      \ar[d, equal]
\\
A \ar[r, "f'f"]              &
D \ar[r, "g'"]  \ar[d, "g''"] &
E \ar[r, "-h''"] \ar[d, "y"]  &
\Sigma A        \ar[d, "\Sigma f"]
\\
&
F \ar[r, equal] \ar[d, "h'"] &
F \ar[r, "h'"] \ar[d, "(\Sigma g)\circ h'"]  &
\Sigma B
\\
&
\Sigma B \ar[r, "\Sigma g"] &
\Sigma C &
\end{tikzcd} \]

Since $(-f,-g,-h)$ and $(-f',-g'',-h')$ were distinguished, $(f,g,h)$ and
$(f',g'',h')$ are anti-distinguished. 

Furthermore, also $(-f'f, -g', h'')$ is isomorphic to $(f'f,-g', -h'')$
(which is distinguished) by $(-\id, \id, \id)$, so also $(f'f, g', -h'')$ is anti-distinguished.
Similarly $(x,-y,-(\Sigma g)\circ h')$ is isomorphic to $(x,y,(\Sigma g)\circ
h')$ by $(\id,\id,-\id)$, so $(-x,y,((\Sigma g)\circ h'))$ is
anti-distinguished.

Which shows $(T5)$ for the class of anti-distinguished triangles.
\end{enumerate}
\end{exercise}

\end{document}
